\documentclass[10pt]{ctexart}
\usepackage{listings}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{xcolor}
\usepackage{xeCJK}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{titletoc}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage[T1]{fontenc}  
\usepackage{textcomp}
\usepackage{lmodern}
%\usepackage{caption}
\usepackage[justification=centering]{subcaption}
\usepackage[justification=centering]{caption}
\usepackage[colorlinks,
            linkcolor=black,
            anchorcolor=black,
            citecolor=black]{hyperref}
\geometry{a4paper,scale=0.8}
\renewcommand\contentsname{Contents}
%\setmonofont[Mapping={}]{Monaco}    %英文引号之类的正常显示，相当于设置英文字体
%\setsansfont{Consolas} %设置英文字体 Monaco, Consolas,  Fantasque Sans Mono
%\setmainfont{Monaco} %设置英文字体
\setmonofont{Consolas}
% 定义可能使用到的颜色
%\setmainfont[BoldFont=SimHei]{SimSun}
\definecolor{CPPLight}  {HTML} {686868}
\definecolor{CPPSteel}  {HTML} {888888}
\definecolor{CPPDark}   {HTML} {262626}
\definecolor{CPPBlue}   {HTML} {4172A3}
\definecolor{CPPGreen}  {HTML} {487818}
\definecolor{CPPBrown}  {HTML} {A07040}
\definecolor{CPPRed}    {HTML} {AD4D3A}
\definecolor{CPPViolet} {HTML} {7040A0}
\definecolor{CPPGray}  {HTML} {B8B8B8}
\lstset{
    columns=fixed,       
    % numbers=left,                                        % 在左侧显示行号
    frame=none,                                          % 不显示背景边框
    backgroundcolor=\color[RGB]{245,245,244},            % 设定背景颜色
    keywordstyle=\color[RGB]{40,40,255},                 % 设定关键字颜色
    numberstyle=\small\color{darkgray},                  % 设定行号格式
    commentstyle=\it\color[RGB]{0,96,96},                % 设置代码注释的格式
    stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},   % 设置字符串格式
    showstringspaces=false,                              % 不显示字符串中的空格
    language=c++,                                        % 设置语言
    morekeywords={alignas,continute,friend,register,true,alignof,decltype,goto,
    reinterpret_cast,try,asm,defult,if,return,typedef,auto,delete,inline,short,
    typeid,bool,do,int,signed,typename,break,double,long,sizeof,union,case,
    dynamic_cast,mutable,static,unsigned,catch,else,namespace,static_assert,using,
    char,enum,new,static_cast,virtual,char16_t,char32_t,explict,noexcept,struct,
    void,export,nullptr,switch,volatile,class,extern,operator,template,wchar_t,
    const,false,private,this,while,constexpr,float,protected,thread_local,
    const_cast,for,public,throw,std},
    emph={map,set,multimap,multiset,unordered_map,unordered_set,
    unordered_multiset,unordered_multimap,vector,string,list,deque,
    array,stack,forwared_list,iostream,memory,shared_ptr,unique_ptr,
    random,bitset,ostream,istream,cout,cin,endl,move,default_random_engine,
    uniform_int_distribution,iterator,algorithm,functional,bing,numeric,},
    emphstyle=\color{CPPViolet},
    basicstyle=\linespread{1}\small\fontspec{Consolas}\ttfamily,
    breaklines=true,
    %xleftmargin=1em,xrightmargin=1em, aboveskip=1em,
    % in the listings package configuration, try:  
    literate={"}{\textquotedbl}1,  
    tabsize=4, keepspaces=true
}
\CTEXoptions[today=old]
\title{Exercises 4}
\author{软件工程一班 \ 张逸松 57号}
\date{\today}

\begin{document}
    \maketitle
    \subsection*{1.18}
        \begin{itemize}
            \item [\textbf{1)}] Suppose there are $2n$ people at first, and after first stage, there will still $n$ people alive. obviously, The $i$-$th$ person in new circle is the $(2i - 1)$-$th$ person in last circle. Let $J(n) = k$, so that $J(2n) = 2k - 1 = 2J(n) - 1$.
            \item [\textbf{2)}] Suppose there are $2n + 1$ people at first, there will $n + 1$ people alive after first stage. Further more, the first person will be killed. At this time, the $i$-$th$ person in new circle (with $n$ people) is the $(2i + 1)$-$th$ person in last circle. Let $J(n) = k$, so that $J(2n) = 2k + 1 = 2J(n) + 1$.
        \end{itemize}

    \subsection*{2.1}
        \textbf{a)} $k = 3$. \quad \textbf{b)} It is not a linear homogeneous recurrence relations with constant coefficient. \quad \textbf{c)} $k = 4$. \quad \textbf{d)} It is not a linear homogeneous recurrence relations with constant coefficient. \quad \textbf{e)} It is not a linear homogeneous recurrence relations with constant coefficient. \quad \textbf{f)} $k = 2$ \quad \textbf{g)} It is not a linear homogeneous recurrence relations with constant coefficient. \quad

    \subsection*{2.10}
        $r^3 - 3r^2 - 3r - 1 = (r - 1){(r + 1)}^2 = 0 \Rightarrow r = -1, 1, 1$
        \begin{equation}
            \begin{aligned}
                a_n &= \alpha_1\cdot(-1)^n + (\alpha_{2,0} + \alpha_{2,1}n)\cdot 1^n \\
                5 &= \alpha_1 + \alpha_{2,0} \\
                -9 &= -\alpha_1 + \alpha_{2,0} + \alpha_{2,1} \\
                15 &= \alpha_1 + \alpha_{2,0} + 2\alpha_{2,1} \\
            \end{aligned}            
        \end{equation}
        \par $\alpha_1 = \frac{19}{2} \quad \alpha_{2,0} = -\frac{9}{2} \quad \alpha_{2,1} = 5$
        \par $a_n = \frac{19}{2}\cdot(-1)^n + (-\frac{9}{2} + 5n)\cdot 1^n$

    \subsection*{2.15}
        \begin{itemize}
            \item [\textbf{a)}] $a_n = \alpha \cdot 2^n + 3^{n+1}$
            \item [\textbf{b)}] $a_1 = 2\alpha + 9 = 5 \Rightarrow \alpha = -2 \Rightarrow a_n = -2 \cdot 2^n + 3^{n+1}$
        \end{itemize}

    \subsection*{4.4}
        \begin{itemize}
            \item [\textbf{a)}] $a_0 = -64, a_1 = 144, a2 = -108, a_3 + 27$ and $a_n = 0$ for all $n \geq 4$.
            \item [\textbf{b)}] $a_0 = 1, a_3 = 3, a_6 = 3, a_9 = 1$ and $a_n = 0$ for others.
            \item [\textbf{c)}] $a_n = 5^n$
            \item [\textbf{d)}] $a_n = (-3)^{n-3}$ for $n \geq 3$, and $a_{0,1,2} = 0$.
            \item [\textbf{e)}] $a_0 = 8, a_1 = 3, a_2 = 2$, and $a_n = 0$ for other odd $n$ while $a_n = 1$ for other even $n$.
            \item [\textbf{f)}] $a_4n = 1$ for $n \geq 1$, $a_{1, 2, 3} = -1$ and $a_0 = 0$.
            \item [\textbf{g)}] $a_n = n - 1$ for $n \geq 2$ and $a_{0, 1}= 0$
            \item [\textbf{h)}] $a_n = \frac{2^{n+1}}{n!}$
        \end{itemize}

    \subsection*{6.2}
    6 solutions.
\end{document}